\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}

%allows links in pdf format and hides the ugly blue boxes around them
\usepackage[hidelinks]{hyperref}

%uses the font Merriweather available from google fonts
\usepackage{fontspec}
\setmainfont{Merriweather}

%removes automatic page numbering
\pagestyle{empty}

\begin{document}

\begin{center}
{\Huge Hector Bennett}
\break

{\small
%Address \\
%Phone Number \\
\href{mailto:hectorbennett@outlook.com}{hectorbennett@outlook.com}
| \href{https://www.hectorbennett.com}{hectorbennett.com} 
| \href{https://www.linkedin.com/in/hector-bennett}{linkedin.com/in/hector-bennett}
}
\end{center}

\section*{Profile}
Highly ambitious Maths graduate and self motivated programmer looking for a career in the technology sector

\section*{Education}
\begin{description}
\item[2013-2016] Mathematics BSc (Hons) (2:1) from King's College London.
\item[2011-2013] A levels in Maths (A*), Further Maths (A*) and Music Technology (A), as well as As levels in English and Art from East Norfolk Sixth Form College.
\end{description}

\section*{Technical Skills}
Reasonably competent with Unix, HTML, CSS, Python, Django, Mathematica, LaTeX, Godot, Git and a variety of creative software.
\begin{itemize}
\item Designed and built a dynamic website using popular frameworks such as bootstrap and django.
\item Created and completed own game project `slimey soccer', effectively utilising git version control.
\item Solved many computational problems on ProjectEuler using python as a fun learning exercise.
\end{itemize}

\section*{Experience}
\begin{description}
\item[Oct 2017 - Present] Bartender - Waterfront Bar and Kitchen
\begin{itemize}
\item Performed under stress in a fast paced environment, effectively managing different tasks simultaneously.
\item Worked well as part of a team, maintaining a positive attitude with both customers and colleagues.
\item Maintained an excellent level of customer service.
\end{itemize}
\item[Aug 2015 - Present] Founder and Manager - *iggle
\begin{itemize}
\item Managed all aspects of a successful club night, including finances and marketing.
\item produced and distributed promotional materials adhering to our brand image both online and in meatspace.
\item Built and maintained constructive relationships with venues.
\item Sold out every event.
\end{itemize}
\end{description}

\end{document}